%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cofounder - CTO} % Job title
    {Pluritech} % Organization
    {Belo Horizonte, Brazil} % Location
    {Oct 2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web App development using Ionic 1/2/3, Angular 1/2/4, HTML, Vanilla Javascript, CSS, Sass, Webpack, Gulp, Grunt, Yeoman.}
        \item {Server management at Digital Ocean, using Ubuntu to server our APIs.}
        \item {Use of Bitbucket Pipelines to CI our projects.}
        \item {Server side development using NodeJS, ExpressJS, PHP, Slim Framework, MongoDB, Elephant.io, Socket.io.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Engineer} % Job title
    {Hangar18} % Organization
    {Belo Horizonte, Brazil} % Location
    {Feb. 2014  - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web App development using Ionic1, AngularJS, HTML, Vanilla Javascript.}
        \item {Server Side with Java Servlets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cofounder} % Job title
    {Cia Web Sites} % Organization
    {Belo Horizonte, Brazil} % Location
    {Feb. 2012 - Dec 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Websites development using WordPress, HTML, Vanilla Javascript, jQuery, PHP and MySQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Internship} % Job title
    {Globalgeo Geotecnologias} % Organization
    {Belo Horizonte, Brazil \& LA, U.S.A} % Location
    {Mar. 2011 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Geoprocessing Web Apps using Python, Django, GeoDjango, PostGIS, PostgreSQL, HTML, Vanilla Javascript, CSS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Internship} % Job title
    {Correios} % Organization
    {Belo Horizonte, Brazil} % Location
    {Sep. 2010 - Mar. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing a GIS to track and analyze the carriers route using PHP, Postgres, PostGIS, CSS, Javascript and HTML.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Student Researcher} % Job title
    {UFMG - Fundep} % Organization
    {Belo Horizonte, Brazil} % Location
    {Feb. 2010 - Aug. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Game developing to ALADIM/FALE/UFMG to study how children learns languages, using Unity3D and Javascript}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
